Globally-centered autocovariances in MCMC

### 2020-07-25 Paper/main.tex
Pushing changes I made during the meeting.

% By proposition 1 in \cite{song1995optimal} 
% \begin{equation} \label{eq:song}
% \Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
% \end{equation}

@@

\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]

@@

\subsection{Autocorrelation} % (fold)
\label{sub:autocorrelation}

% subsection autocorrelation (end)
For any component $i$, the autocorrelation is
\[
\rho^{(i)}(k) = \dfrac{\Gamma^{(i)}(k)}{\Gamma^{(i)}(0)}\,,
\]
and is particularly useful for visualizing the serial correlation in components of the Markov chain. The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation. 
\[
\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}
\]
{\color{blue} Add more about autocorrelation}

@@

We are interested in Markov chain average and therefore, throughout this paper, we will deal with the function $g(X) = X$. To assess the reliability of our simulations, we are interested in Monte Carlo error, i.e. $\bar{\bar{X}} - \mu$. The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
%
\[
\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
\]

@@

Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = \dfrac{1}{n}\sum_{t=1}^{n}X_t$ is the MCMC average. Let $w_k$ denote the lag-window at lag-k, i.e. $w_k = w_n(k/b_n)$. The alternate formulation for MSVE is given by
%
\[
    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
\end{pmatrix}^T
\]

@@

\[
\hat{\Sigma}_{S,s} = \dfrac{1}{n}B^T T(w) B \qquad \textrm{ where } B = 
\begin{pmatrix}
    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}
\end{pmatrix}^T
\].

@@

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m}\,.
\end{align*}
%
 We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
 \begin{equation} \label{eq:G-_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] \, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$. Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\color{red}\mathcal{O}}(1/n)$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
\begin{align*}
& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
\end{align*}
In the presence of positive correlation, the leftover term is positive.

@@

>>>>

By proposition 1 in \cite{song1995optimal} 
\begin{equation} \label{eq:song}
\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
\end{equation}

@@

{\color{blue} Below is a remark}
\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2} + o(n^{-2})
\]

@@

% \subsection{Autocorrelation} % (fold)
% \label{sub:autocorrelation}

% subsection autocorrelation (end)
{\color{blue}  Autocovariances will be used implictly in SVE estimators. But they are explicitly important in ACF plots via autocorrelations.

Notation in the appendix is $\Gamma^{ii}_{G,s}$
}

For any component $i$, the autocorrelation is
\[
\rho^{(i)}(k) = \dfrac{\Gamma^{(i)}(k)}{\Gamma^{(i)}(0)}\,,
\]
and is particularly useful for visualizing the serial correlation in components of the Markov chain. The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation. 
\[
\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}
\]
{\color{blue} Add more about autocorrelation. Refer to Figure 2 above and the impacts of the correlation methods. }

@@

We are interested in Markov chain average and therefore, throughout this paper, we will deal with the function $g(X) = X$. To assess the reliability of our simulations, we are interested in Monte Carlo error, i.e. $\bar{\bar{X}} - \mu$. The sampling distribution for Monte Carlo error is available via Markov chain CLT (\cite{jones2004markov}) if there exists a positive definite matrix $\Sigma$ such that
%
{\color{blue} }
\[
\sqrt{n}(\bar{X}_s-\mu) \xrightarrow{d} N(0,\Sigma)
\]

@@

Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = n^{-1}\sum_{t=1}^{n}X_t$ is the MCMC average. Let $w_k$ denote the lag-window at lag-k, i.e. $w_k = w_n(k/b_n)$. The alternate formulation for MSVE is given by
%
\[
    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
\end{pmatrix}^T
\]

@@

\[
\hat{\Sigma}_{S,s} = \dfrac{1}{n}B^T T(w) B \qquad \textrm{ where } B = 
\begin{pmatrix}
    X_{s1} - \overline{\overline{X}} \; \dots \; X_{sn} - \overline{\overline{X}}\end{pmatrix}^T
\].

@@

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation {\color{blue} + add small order term. Confirm with Priestly. }
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using \eqref{eq:priestly}, \eqref{eq:acf_2}, \eqref{eq:acf_3}, and \eqref{eq:acf_4} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t=1}^{|k|}\mathbb{E}[A_{1t}^T] + \sum\limits_{t=n-|k|+1}^{n}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{|k|}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{|k|}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m}\,.
\end{align*}
%
 We can use the results of \cite{song1995optimal} given in \eqref{eq:song} to expand $\Var(\bar{X}_1)$. Expectation of $\hat{\Gamma}_{G,s}(k)$ can then broken down as following,
 \begin{equation} \label{eq:G-_expec_breakdown}
     \mathbb{E}\left[\hat{\Gamma}_{G,s}(k)\right] = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) + O_1 + O_2\,.
 \end{equation}
%
where,
\begin{align*}
    O_1 &= -\dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right)\right] \, ,\\
    O_2 &= -\dfrac{1}{m}\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o(n^{-2})
\end{align*}
%
We observe that both $O_1 \textrm{ and } O_2$ are small order terms that converge to 0 as $n \to \infty$. Here, $O_1 = (-\abs{k}/n)\mathcal{O}(1/n) \textrm{ and } O_2 = {\color{red}\mathcal{O}}(1/n)$. For a diagonal element of $\Gamma$,
% We observe that this expectation result is very similar to equation \ref{eq:priestly} from \cite{priestley1981spectral} for the asymptotically unbiased estimator of autocovariance except for an additional positive bias term. This helps in countering the inherent negative bias in $\hat{\Gamma}(k)$ and give more informative estimates of autocovariance.  Although, bias term for a fixed $k$ is $o(1)$, it increases with $k$. We have explicitly written the end effect term arising from using the estimator $\bar{\bar{X}}$ for $\mu$. These are small order terms that vanish as $n \to \infty$.
%
\begin{align*}
& \E \left[ \hat{\Gamma}_{G,s}^{ii}\right]\\
& = \mathbb{E}\left[\hat{\Gamma}^{ii}_{s}(k)\right] - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1} \left[\Gamma^{ii}(h)^T + \Gamma^{ii}(h) \right] \right) - \left(2-\dfrac{1}{m}\right) \Var(\overline{X}_1)^{ii}\right] - \dfrac{\Var(\overline{X}_1)^{ii}}{m}\,.
\end{align*}
In the presence of positive correlation, the leftover term is positive.

@@

\subsection{G-SVE Bias}

\begin{proof}[Proof of theorem \ref{th:G-SVE_bias}]
The convoluted end effect terms in theorem \ref{th:G-_expec} are all essentially $\mathcal{O}(1/n)$. We are interested in finding the asymptotic bias here. Therefore we can write the expectation of replicated autocovariance in form of equation \ref{eq:G-_expec_breakdown} as,
\begin{align*}
&\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right]\\
&  = \left(1- \dfrac{|k|}{n}\right)\Gamma(k) - \dfrac{|k|}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\overline{X}_1)}{m} \\
& = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2  \numberthis \label{eq:G-_bias2}  \,.
\end{align*}
%
% \begin{equation} \label{eq:G-_bias2}
% \mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] = \left(1 - \dfrac{\abs{k}}{n}\right)\Gamma(k) + O_1 + O_2    \,.
% \end{equation}
%
where both $O_1 \textrm{ and } O_2$ are the small order terms. By our assumptions, $\sum_{h=-\infty}^{\infty}\Gamma(h) < \infty$, so $O_1 = o(1/n) \text{ and } O_2 = o(1/n)$.  Consider the G-SVE estimator,
\begin{align*}
    &\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right]\\
    &= \sum_{k=-n+1}^{n-1} w\left(\dfrac{k}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G-}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)\\
    &= \sum_{k=-n+1}^{n-1}  w\left(\dfrac{k}{b_n}\right)\left[\left(1-\dfrac{|k|}{n}\right)\Gamma(k) +O_1 + O_2\right]  - \sum_{k=-\infty}^{\inf}\Gamma(k)\\
    &= \sum_{k=-n+1}^{n-1} \left[ w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k)\right]  - \sum_{k=-\infty}^{\infty}\Gamma(k) + \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k}{b_n}\right)\left(O_1 + O_2\right)\right] \\ 
    & = P_1 + o \left( \dfrac{1}{n} \right)\,
\end{align*}
%
where 
\begin{align*}
P_1 & = \sum\limits_{k=-n+1}^{n-1}\left[w\left(\dfrac{k}{b_n}\right)\left(1-\dfrac{|k|}{n}\right)\Gamma(k) \right] - \sum\limits_{k=-\infty}^{\infty}\Gamma(k)\,.
% P_2 &= \sum_{k=-n+1}^{n-1}\left[  w\left(\dfrac{k }{b_n}\right)\left(O_1 + O_2\right)\right]\,.
\end{align*}
%
We first solve for term $P_1$ by breaking it into three parts as in \cite{hannan2009multiple}. Note that notation $A = o(z)$ for matrix $A$  implies $A^{ij} = o(z)$ for each element of the matrix $A$. Consider,
\begin{equation}
\label{eq:P1_decomp}
P_1 = -\sum_{|k|\geq n}\Gamma(k)  -  \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k)- \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{n}\right)\right)\Gamma(k)\,.  
\end{equation}
%
We deal with the three subterms of term $P_1$ individually. First,
%    
\begin{align*}
 {-\sum_{|k|\geq n}\Gamma(k)} &\leq  \sum_{|k|\geq n} \abs{\dfrac{k}{n}}^q   \Gamma(k) = \dfrac{1}{b_n^q}\abs{\dfrac{b_n}{n}}^q \sum_{|k|\geq n}|k|^q  \Gamma(k) = o\left(\dfrac{1}{b_n^q}\right)\,, \numberthis \label{eq:P1_first}
\end{align*}
%
since $\sum_{|k|\geq n}|k|^q \Gamma(k)  < \infty$. Next,
%
\begin{align*}
 \sum_{k = -n+1}^{n-1}w\left(\dfrac{k}{n}\right)\dfrac{|k|}{n}\Gamma(k)   &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  \,.
\end{align*}
For $q\geq 1$,
\begin{align*}
\dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k) &\leq \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k) = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n} C\sum_{k = -n+1}^{n-1}|k|^q  \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right)\,.
\end{align*}

For $q <1$,
\begin{align*}
   \dfrac{C}{n}\sum_{k = -n+1}^{n-1}|k|  \Gamma(k)  &\leq C\sum_{k =-n+1}^{n-1}\abs{\dfrac{k}{n}}^q  \Gamma(k)  = \dfrac{1}{b_n^q}\dfrac{b_n^q}{n^q} C \sum_{k =-n+1}^{n-1}|k|^q \Gamma(k)  = o\left(\dfrac{1}{b_n^q}\right) \, .
\end{align*}
So,
\begin{equation}
\label{eq:P1_second}
 \sum_{k = -n+1}^{n-1}w\left(\dfrac{|k|}{n}\right)\dfrac{|k|}{n}\Gamma(k) = o \left(\dfrac{1}{b_n^q} \right)
\end{equation}
Lastly, by our assumptions, for $x \to 0$
\[
\dfrac{1 - w(x)}{\abs{x}^q} = k_q + o(1)\,.
\]
For $x = k/b_n$, $\abs{k/b_n}^{-q}(1-w(k/b_n))$ converges boundedly to $k_q$ for each $k$.
 % where $k_q$ is specific to the lag-window used. Taking the limiting value, we have
     % \[
     % \lim_{n \to \infty}\sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)\Gamma(k) = -\dfrac{k_q \Phi^{(q)}}{b_n^q}
     % \]
So,
\begin{align*}
     \sum_{k = -n+1}^{n-1}\left(1-w\left(\dfrac{k}{b_n}\right)\right)\Gamma(k) &= -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}  \left(\dfrac{|k|}{b_n}\right)^{-q} {\left(1-w\left(\dfrac{|k|}{b_n}\right)\right)}|k|^q \Gamma(k) \\
     & = -\dfrac{1}{b_n^q}\sum_{k = -n+1}^{n-1}   \left[k_q + o(1) \right]|k|^q \Gamma(k) \\
     & = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right) \numberthis \label{eq:P1_third}\,.
\end{align*}
%
 % Finally, we will solve for $P_2$. Note that $O_2$ is independent of $k$. We will write $O_1$ as $(\abs{k}/n)\mathcal{O}(1/n)$ and $O_2$ as $\mathcal{O}(1/n)$. We will find an upper bound and prove that it is $\mathcal{O}\left(n^{-1}\right)$:
 % \begin{align*}
 %     &  \sum_{k=-n+1}^{n-1}w\left(\dfrac{|k|}{b_n}\right)\left[ O_1 + O_2 \right]  \\
 %     & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)O_1} + \abs{O_2}\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{|k|}{b_n}\right)} \\
 %     &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{|k|}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\\
 %     % &= \mathcal{O}\left(\dfrac{1}{n}\right) 2\pi W_n \\
 %     &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
 % \end{align*}
  %
%
Using \eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:P1_decomp}, we get
\[
\mathbb{E} \left[\hat{\Sigma}_{G-SVE} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
\]
which completes the result.
%
 % We have shown that all, but one, terms are $o(1/b_n^q)$. Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms. This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu$ in our replicated autovariance estimator. Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu$ contributes only $o(1)$ terms. 
\end{proof}
